---
title: "Speakers in the Congressional Recored"
subtitle: 
author: ""
output:
  html_document:
    highlight: zenburn
    toc: true
    toc_float: true
    code_folding: hide
editor_options: 
  chunk_output_type: console
---


```{r global.options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      cache = FALSE, 
                      fig.width=8.5, 
                      split = T,
                      fig.align = 'center', 
                      fig.path='figs/',
                      warning=FALSE, 
                      message=FALSE)


library(tidyverse)
library(purrr)
library(here)
library(rvest)
library(readr)
library(magrittr)
library(tidytext)
library(knitr)
library(kableExtra)
library(here)
library(crayon)

library(ggplot2); theme_set(theme_minimal())
  options(
    ggplot2.continuous.color = "viridis",
    ggplot2.continuous.fill = "viridis"
  )
  scale_color_discrete <- function(...)
    scale_color_viridis_d(...)
  scale_fill_discrete <- function(...)
    scale_fill_viridis_d(...)
  
kablebox <- . %>% 
  head(100) %>%
  knitr::kable() %>% 
  kable_styling() %>% 
  scroll_box(height = "400px")
```

# Data scraped in [scraper vignette](articles/scraper.html).

# Parse the Congressional Record

### 0. Metadata from html
```{r html-metadata, cache = TRUE}
library(congressionalrecord)
# Note, we don't need this metadata to parse the files
# metadata
load(here::here("data", "cr_metadata.Rdata"))

# clean up data for plot clarity
cr_metadata %<>% 
  mutate(year = str_sub(date, 1,4) %>% as.numeric(),
         chamber = section %>% 
           str_remove("-.*") %>% 
           str_to_title() %>%
           str_replace("Extensions", "Extensions of Remarks")) 
```


### 1. Metadata from file names

```{r file-metadata, cache=TRUE}
# directory for bulk cr files 
bulk_directory <- here::here("data", "htm") #%>% str_replace("cr", "cr_bulk")

# load cr text file names
cr_file <- list.files(bulk_directory)

file.size(here::here("data", "htm", cr_file[1:10] ))

# cr %<>% filter(file.info)

# extract date from file name
cr <- tibble(file = cr_file,
            year = str_extract(cr_file, "[0-9]{4}") %>% as.numeric(),
            date = str_extract(cr_file, "[0-9]{4}-[0-9]{2}-[0-9]{2}") %>% 
              as.Date() ) 

# get congress from year 
cr %<>% mutate(congress = as.numeric(round((year - 2001.1)/2)) + 107) # the 107th congress began in 2001

# extract chamber from URL 
cr %<>% mutate(chamber = str_extract(file, "Pg.") %>% 
                str_remove("Pg") %>%
                str_replace("E", "Extensions of Remarks") %>% 
                str_replace("H", "House") %>% 
                str_replace("S", "Senate") )

# reconstruct URLs from file names
cr %<>% mutate(url_txt = str_c("https://www.congress.gov/", congress, "/crec/", 
                              date %>% str_replace_all("-", "/"), 
                          "/modified/", 
                          file))
```



### 2. Read in text

> NOTE: I'm just using a sample of documents for now.

```{r}
library(congressionalrecord)
d <- cr

#FIXME
# just using a few documents for now

d %<>% top_n(2, date)

# d <- slice_head(cr, n = 30)
# /FIXME




## test
# file <- d$file[1]
# head_text(file)
# all_text(file)

congressionalrecord::head_text(d$file[1])

# the first bit of text
d$text_head <- d$file %>% map_chr(possibly(congressionalrecord::head_text, otherwise = "")) 

# fill in procedural roles
d %<>% 
  mutate(process = str_extract(text_head, "^(ANNOUNCEMENT|RECESS|PRAYER|PLEDGE|MESSAGE|EXECUTIVE MESSAGE|EXECUTIVE COMMUNICATION|EXECUTIVE AND OTHER COMMUNICATION|MEASURE|ADJOURNMENT|DESIGNATION|THE JOURNAL|RESIGNATION|ELECTING|CONSTITUTIONAL|ADDITIONAL SPONSORS|SWEARING IN|MOMENT OF SILENCE|SENATE COMMITTEE MEETING|BUDGETARY|EFFECTS|REAPPOINTMENT|APPOINTMENT|RECALL|COMMUNICATION|REMOTE COMMITTEE PROCEEDINGS|REMOTE VOTING||ENROLLED BILL|ADDITIONAL COSPONSORS|DISCHARGED NOMINATION|CONFIRMATION|JOINT RESOLUTION|SENATE ENROLLED BILLS|PUBLICATION|EXPLANATORY STATEMENT|WITHDRAWAL)") )  



# order by date (just for presentation)
d %<>% arrange(date) %>% arrange(rev(date))
```



### 3. Extract speaker names from text with `extract_names()`

```{r extract}
# Extract speaker names
## Test
# file <- d$file[22]
# extract_names(d$file[22])

d %<>%
  mutate(speaker = file %>% map_chr(possibly(extract_names, otherwise = "404error"))) %>% 
  mutate(speaker = ifelse(speaker == "", "404error", speaker))

dim(d)
```

---

#### Multiple speakers?

```{r, cache=FALSE}
d %>% 
  filter(str_detect(speaker, ";")) %>% 
  select(speaker, url_txt) %>% kablebox()
```

---

#### No speaker? 

```{r, cache=FALSE}
d %>% 
  filter(is.na(speaker)|speaker == "404error") %>% 
  select(speaker,  text_head, url_txt) %>% kablebox()
```


### 4. Parse texts with multiple speakers with `parse_text()`

```{r}
# for testing
# speaker_list <- d$speaker[22] 
# file <- d$file[22]

## test
# parse(d$speaker[30], d$file[30])


dim(d)
d %<>% parse_text()

d %>% 
  filter(!speaker == "404error", 
         !is.na(speaker) ) %>% 
  select(speaker, text_head, url_txt) %>% kablebox()
```

---

### Most frequent speakers from `r min(d$date)` to `r max(d$date)`

```{r, cache=FALSE}
d %>% 
  count(speaker, sort = T) %>% kablebox()
```



# Match with voteview 

```{r}
library(legislators)

# get congress from year 
d %<>% mutate(congress = as.numeric(round((year - 2001.1)/2)) + 107) # the 107th congress began in 2001

# clean up speaker names and add chamber titles for better matching
d %<>% mutate(chamber = ifelse(
  chamber == "Extensions of Remarks" &
    str_detect(text_head, "(Mr|Mrs|Ms|Miss)\\. Speaker\\,|in the house of representatives"), "House", "Senate"),
              speaker = speaker %>% 
    str_remove("(^|;)(Mr|Mrs|Ms|Miss|HON)(\\.| )") %>% 
    str_squish())

d %<>% mutate(speaker =
               ifelse(row_number() > 1 & str_detect(lag(speaker),
                                 speaker), 
                      lag(speaker),
                      speaker)) 

# fixme this is a artifact of extractmembername's original use
d %<>% mutate(agency = congress)

d1 <- d %>% extractMemberName(col_name = "speaker", members = members)

d1 %>% 
  select(speaker, bioname, icpsr, chamber) %>%
  distinct() %>% kablebox()
```


# Save text parsed by member name with `cr_write()`


```{r, eval=FALSE}
# FOR TESTING 
# cr_date <- "2018-02-06"

## Many days of the CR (e.g. feburary 2020)
dates <- cr %>% #filter(str_detect(date, "2016-02")) %>% 
  distinct(date)
# cr_date <- dates$date[1]

## One day of the CR
# cr_write("2020-02-06")

## Many days of the CR (e.g. feburary 2020)
dates <- cr %>% #filter(str_detect(date, "2016-02")) %>% 
  distinct(date)

# Testing 
cr_date <- dates$date[3]
# cr_date <- "2020-09-23"
cr_write(cr_date)

# save all
walk(dates$date, cr_write)
```

## Directory structure for parsed txt
```{r}
# fill in empty
d1 %<>% 
  mutate(file = file %>% replace_na("CREC-missing"),
         icpsr = icpsr %>% as.integer() %>% replace_na(00000))

d1 %<>% mutate(path = str_c("data", 
               "txt", 
               year, 
               icpsr, 
               str_c(file %>% str_remove(".htm"), 
                     "-", match_id, "-", icpsr, ".txt"),
               sep = "/"  ))

d1 %>% 
  select(bioname, path) %>% kablebox()
```

